Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-08 trunk/lids/twittersearchwrap/paper/paper.tex
added list of hashtags

%\newcommand{\nop}[1]{}

@@

@@

Topics trending worldwide and in Germany at Twitter retrieved on February 24th
17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
constitute a basis of input search terms for our evaluation of the Twitter
Search Wrapper.

@@

The goal of our evaluation was to examine the stability of the entity
annotations over time. To achieve this, we have repeatedly executed the same set
of queries and saved the returned data. Two methods for this data acquisition
were identified: \begin{definition}[Data Acquisition Methods]
\begin{itemize}
\item Temporal Sliding Window: The query is executed and the n most
recent results are retrieved every t minutes. The Temporal Sliding Window method
may lead to duplicate messages in the retrieved documents, but needs to handle much less data and
allows for an analysis over larger time frames.
\item k-item Sliding Window: The k-item Sliding Window methods retrieves all
messages that match the query exactly one time. Each time k new messages are
available matching the given query a document containing those k messages
is retrieved. This method can lead to high data volume and needs constant
monitoring of recently posted messages matching the search term.
\end{itemize}
\end{definition}

Using the retrieved trending topics given in Table \ref{tbl:terms}
as input queries for the evaluation, the set of queries was executed twice
per hour using the Temporal Sliding Window method for data acquisition in a 24
hour time frame starting from the moment the topics were identified as trending topics.  We have then evaluated the results with respect to several measures:

\begin{definition}[Evaluation Measures]
Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with sets of entities $E_1,\ldots,E_n$, we define:
\begin{itemize}
	\item The average disjoint time $adt$ for a query is the average time that has to lie between two result sets in order to obtain disjoint results: $$adt(q)=\frac{\sum_{i=1}^{n}t_{i+1}-t_i}{n-1}$$
	A high $adt(q)$ means that new messages that match the query $q$ are not generated very often. If new messages matching the query $q$ are frequently published, then the $adt(q)$ is low.
	\item The global stability $gs$ of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{|\bigcap_{i=1}^{n}E_i|}{|\bigcup_{i=1}^{n}E_i|}$$
	A value of $gs(q)$ of $1$ means that the set of entities is the same at each point in time $t_i$. On the other hand, a value of $0$ means that at least two of the sets of entities, with which the results were annotated, are disjoint.
	\item The time stability $ts$ for a query $q$ at time $t_i$ is the fraction of entities which are unchanged between the result set at $t_{i-1}$ and $t_i$:
	$$ts(q,t_i)=\begin{cases} |E_i| & i=1 \\
														\frac{|E_{i-1}\cap E_i|}{|E_{i-1}\cup E_i|} & i>1\end{cases}$$
	Here again, a value of $1$ means that the two sets of entities are identical, a value of $0$ means they are disjoint.
	\item The stability for a single term is defined as the fraction of result sets for a query $q$ in which it occurs: 
$$sts(q,t)=\frac{|\{i|t\in E_i\}|}{n}$$
	If the value of $sts$ is $1$ the term occurs in all of the result sets for the query, if it is close to $0$ it occurs in few result sets.
\end{itemize}
\end{definition}

>>>>

\newcommand{\nop}[1]{}

@@

\nop{
http://tagdef.com/ has a list of popular tags
}

@@

Topics trending worldwide and in Germany on Twitter retrieved on February 24th
17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
constitute a basis of input search terms for our evaluation of the Twitter
Search Wrapper.

We have sampled the Twitter message feed using Twitter's Streaming API for one minute twice an hour from 2011-03-03 to
2011-03-06.
The top-50 hashtags dervied from the aggregate sample are listed in Table \ref{tbl:hashtags}.
We then recorded search results for these 50 hashtags during the course of 24 hours (2011-03-07).

\begin{table}[ht*]
\centering
\begin{tabular}{ l|l }
Hashtag & Count  \\
\hline
ff &     460 \\
np &     172 \\
nowplaying &     144 \\
winning &     134 \\
fb &     105 \\
rt &      83 \\
mentionke &      61 \\
blackpeoplemovies &      57 \\
tigerblood &      56 \\
thataintwinning &      53 \\
fail &      53 \\
teamfollowback &      52 \\
iftwitterwashighschool &      51 \\
bieberfact &      51 \\
news &      46 \\
jobs &      45 \\
libya &      44 \\
followmejp &      44 \\
partiu &      41 \\
sougofollow &      39 \\
damnitstrue &      39 \\
tilltheworldends &      37 \\
soalcinta &      35 \\
nicovideo &      35 \\
quran &      33 
\end{tabular}
\begin{tabular}{ l|l }
Hashtag & Count  \\
\hline
nw &      32 \\
quote &      31 \\
shoutout &      30 \\
jfb &      30 \\
carnaval &      27 \\
tfb &      26 \\
followme &      26 \\
followfriday &      25 \\
follow &      24 \\
egypt &      23 \\
retweet &      22 \\
fact &      22 \\
win &      20 \\
tweetmyjobs &      20 \\
music &      20 \\
in &      20 \\
imagine &      20 \\
nowwatching &      19 \\
cumannanyaindonesia &      19 \\
twexit &      18 \\
lcv &      18 \\
fui &      18 \\
bot &      18 \\
nemuritsuzuketeshinu &      17 \\
fato &      17 \\
\end{tabular}
\caption{Popular hashtags sampled during a three-day period.}\label{tbl:hashtags}
\end{table}

@@

The goal of our evaluation was to examine the stability of the entity
annotations over time. To achieve this, we have repeatedly executed the same set
of queries and saved the returned data. Two methods for this data acquisition
were identified: \begin{definition}[Data Acquisition Methods]
\begin{itemize}
\item {\bf Temporal Sliding Window}\newline The query is executed and the n
most recent results are retrieved every t minutes. The Temporal Sliding Window
method may lead to duplicate messages in the retrieved documents, but needs to
handle much less data and allows for an analysis over larger time frames.
\item {\bf k-item Sliding Window}\newline  The k-item Sliding Window methods
retrieves all messages that match the query exactly one time. Each time k new messages are
available matching the given query a document containing those k messages
is retrieved. This method can lead to high data volume and needs constant
monitoring of recently posted messages matching the search term.
\myremark{todo}{Nicht genau machbar wegen Zeitpunkt, wann Lookup gemacht werden soll, nicht bekannt}
\end{itemize}
\end{definition}

We considered the trending topics on Twitter a good set of input queries for
our evaluation approach. Trending topics often cover a variety of recently
talked about topics which due to its recent nature may be of high interest for
further processing. Using the retrieved trending topics given in Table
\ref{tbl:terms} as input queries for the evaluation, the set of queries was executed twice per hour using the Temporal Sliding Window method for data acquisition in a 24 hour time frame starting from the moment the topics were identified as trending topics. We chose the Temporal Sliding Window method for data acquisition because of the expected data volume generated by trending topics as search terms and the long term nature of our evaluation approach. We have then evaluated the results
with respect to several measures:

\begin{definition}[Evaluation Measures]
Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with sets of entities $E_1,\ldots,E_n$, where each result set $R_i$ consists of twitter messages $r_i1,\ldots,r_iK$ with time stamps $t_i1,\ldots,t_iK$ we define:
\begin{itemize}
	\item The average update time within a result set $aut(R_i)$ for a query is the average time that lies between messages that match the query which produced the search result: $$aut(R_i)=\frac{\sum_{j=1}^{n}t_{i,j+1}-t_{i,j}}{K-1}$$
	A high $aut(R)$ means that new messages that match the query are not generated very often. If new messages matching the query are frequently published, then the $adt(R)$ is low.

	The mean $aut(q)$ and the variance $autv(q)$ of the $aut(R_i)$ can be used to describe update properties for the result sets that are generated for a given query. E.g. if for a given query $aut(q)$ is high and $autv(q)$ is low, then the rate at which messages are published is stable at a quite low level.
%	\item The global stability $gs$ of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{|\bigcap_{i=1}^{n}E_i|}{|\bigcup_{i=1}^{n}E_i|}$$
%	A value of $gs(q)$ of $1$ means that the set of entities is the same at each point in time $t_i$. On the other hand, a value of $0$ means that at least two of the sets of entities, with which the results were annotated, are disjoint.
	\item The stability for a single term is defined as the fraction of result sets for a query $q$ in which it occurs: 
$$sts(q,t)=\frac{|\{i|t\in E_i\}|}{n}$$
	If the value of $sts$ is $1$ the term occurs in all of the result sets for the query, if it is close to $0$ it occurs in few result sets.
	\item The time stability $ts$ for a query $q$ at time $t_i$ is the fraction of entities which are unchanged between the result set at $t_{i-1}$ and $t_i$:
	$$ts(q,t_i)=\begin{cases} |E_i| & i=1 \\
														\frac{|E_{i-1}\cap E_i|}{|E_{i-1}\cup E_i|} & i>1\end{cases}$$
	A value of $1$ means that the two sets of entities are identical, a value of $0$ means they are disjoint.

	The variance of time stabilities $ts(q,t_i)$ over all $t_i$ helps to determine whether the rate at which the found entities change is rather stable or whether it is changing a lot over time.
\end{itemize}
\end{definition}
